Modeling an Economy with Policy Gradients

### 2019-12-06 paper/paper.tex
Corrected paper RL section with logs, pre-advantage AC

\usepackage{float}
\usepackage{cite}

@@

\subsection{RL Algorithms******}
We worked within the realm of policy gradient methods; we chose this family of algorithms

[exploration strategy is built in?]

with large action spaces.

As framed, our problem contains large — in fact, high dimensional — state spaces. Specifically, the dimension of a given state is $s_s = 2 \cdot (\text{number of firms}) + (\text{number of people})$. Furthermore, while the values in each dimension were integers, they could take on a wide range of values. Therefore, in every policy, we use neural network architectures to convert a given state to a vector, containing log probabilities of taking each action. In empirical testing, if $s_a$ is the number of possible actions, we've seen that the following architecture is a simple framework that still yields convergence in our context:
\begin{itemize}
  \item Input layer with state input, of dimension $s_s$. State values are unnormalized.
  \item Hidden layer with tanh activation, of dimension $\left\lfloor \sqrt{s_s \, s_a} \right\rfloor$
  \item Output layer with tanh activation, followed by log softmax, of dimension $s_a$
\end{itemize}
During training, we generally use a learning rate of $\alpha = 0.01$.

\subsubsection{REINFORCE Policy Gradient******}

>>>>

\usepackage{float}
\usepackage{cite}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

@@

\subsection{RL Algorithms******}
Following the literature we reviewed, we worked within the realm of policy gradient methods; we also choose this family of algorithms because they have stronger convergence guarantees than value-based RL methods (albeit potentially to local optimum that are not global optimum).
\newline\newline
As framed, our problem contains large — in fact, high dimensional — state spaces. Specifically, the dimension of a given state is $s_s = 2 \cdot (\text{number of firms}) + (\text{number of people})$. Furthermore, while the values in each dimension were integers, they could take on a wide range of values. Therefore, in every policy, we use neural network architectures to convert a given state to a vector, containing log probabilities of taking each action. In empirical testing, if $s_a$ is the number of possible actions, we've seen that the following architecture is a simple framework that still yields convergence in our context:
\begin{itemize}
  \item Input layer with state input, of dimension $s_s$. State values are unnormalized.
  \item Fully-connected hidden layer with tanh activation, of dimension $\left\lfloor \sqrt{s_s \, s_a} \right\rfloor$
  \item Fully-connected output layer with tanh activation, followed by log softmax, of dimension $s_a$
\end{itemize}
During training, we generally use a learning rate of $\alpha = 0.01$.

\subsubsection{REINFORCE Policy Gradient}
Perhaps the simplest policy gradient method is the REINFORCE algorithm. This algorithm uses a Monte Carlo-type approach to gathering training data. We manually specify the length of the episode, generally using $T = 100$.
\begin{algorithm}
\caption{REINFORCE Policy Gradient}\label{euclid}
\begin{algorithmic}[1]
\Procedure{REINFORCE}{}
\State $\text{Initialize policy network parameters }\theta$
\For {$i = 1, 2, \ldots, M$}
\State $\text{Follow current policy to obtain trajectory }$\newline\phantom{======}$\{s_1, a_1, r_1, \ldots, s_T, a_T, r_T\}$.
\For {$t = 1, 2, \ldots, T$}
\State $\text{Compute }v_t = \sum_{i = t}^n \gamma^{i- t} r_i$.
\State $\text{Update } \theta \leftarrow \theta + \alpha \nabla_{\theta}\log\pi_{\theta} (s_t, a_t) v_t$
\EndFor
\EndFor
\State \Return {$\theta$}
\EndProcedure
\end{algorithmic}
\end{algorithm}
This algorithm runs reasonably quickly per episode. However, we also need to run more episodes because:
\begin{itemize}
  \item Agents only update the parameters once per episode.
  \item In many contexts, vanilla REINFORCE has been known to suffer from high variance in the losses from episode to episode.
  \item In our multi-agent problem, the environment dynamics constantly change because every agent responds to each timestep in the markets.
\end{itemize}

\subsubsection{Q Actor-Critic}
An alternative family of policy gradient methods is the \textit{actor-critic} family. In these algorithms, the actor component computes the log probabilities $\log \pi_{\theta}(s, a)$ while the critic component approximates the functions $Q(s, a)$. We consider this set of algorithms because while they carry the convergence advantages of general policy gradient methods, they also approximate the Q-values with better sample efficiency. In our context, we again use neural networks with one hidden layer each for both the actor and critic. 
\begin{algorithm}
\caption{Q Actor Critic}\label{euclid}
\begin{algorithmic}[1]
\Procedure{Actor\_Critic}{}
\State $\text{Initialize policy and Q-network parameters }\theta, \omega$
\For {$i = 1, 2, \ldots, M$}
\State $\text{Initialize state and action }s_1, a_1 \sim \pi_{\theta}(a|s_1)$.
\For {$t = 1, 2, \ldots, T-1$}
\State Record reward $r_t$ and next state $s_{t+1}$
\State Sample the next action $a_{t+1} \sim \log \pi_{\theta}(a|s_{t+1})$
\State $\text{Update } \theta \leftarrow \theta + \alpha_{\theta} Q_{\omega}(s_t,a_t) \nabla_{\theta} \pi_{\theta} (s_t, a_t)$
\State $\text{Compute temporal difference error: }\delta_t = r_t + \gamma Q_{\omega}(s_{t+1}, a_{t+1}) - Q_{\omega}(s_{t}, a_{t})$
\State $\text{Update } \omega \leftarrow \omega + \alpha_{\omega} \delta_t \nabla_{\omega} Q_{\omega} (s_t, a_t)$
\EndFor
\EndFor
\State \Return {$\theta, \omega$}
\EndProcedure
\end{algorithmic}
\end{algorithm}
In the current version we have implemented, the

[************** Q-network doesn't converge, maybe because we have an unstable target, requiring a target network]
